Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2019-12-02 xrb/paper.tex
finish my pass

In order to satisfy these requirements whilst allowing the simulations to be computationally feasible, we used several approximations: a higher than normal rotation rate, a boosted flame, a simplified reaction network, and a 2.5D model for the flow. The first two of these were used to reduce the model's spatial and temporal scales. Using the simulation framework developed here, these both can be relaxed in the future, at the cost of more computer time. The same goes for 2.5D
vs.\ full 3D---the only difference is computer time, and our future
calculations will explore the 3D evolution and compare to the 2.5D simulations presented here. In particular,
in 3D we will be able to explore shear instabilities at the flame front.  We can also capture the 
baroclinic instability \citep{Cavecchi2019} and the competition between it and shear.
Larger networks are a straightforward change, and already supported in
\castro\ using the \pynucastro\ framework~\citep{pynucastro} and JINA
ReacLib rate database~\citep{reaclib}.

@@

In addition to exploring other aspects of the XRB physics, there are several changes to the algorithm used to
model these XRBs we will pursue.  First, as shown in \citet{castro-sdc}, we have
developed a fourth-order (in space and time) method for coupling
hydrodynamics and reactions that should greatly improve the accuracy
of the simulations.  We expect that by using this new high-order
algorithm we can drop a level of refinement from the simulations while
still accurately modeling the evolution.  We have also ported
\castro\ to GPUs, giving an order of magnitude performance boost on
nodes with both CPUs and GPUs.  The GPU-enabled algorithm will
increase the performance, allowing us to run bigger domains and/or
eliminate the boosting used here.

>>>>

In order to satisfy these requirements whilst allowing the simulations
to be computationally feasible, we used several approximations: a
higher than normal rotation rate, a boosted flame, a simplified
reaction network, and a 2D axisymmetric model for the flow. The first two of
these were used to reduce the model's spatial and temporal
scales. Using the simulation framework developed here, these both can
be relaxed in the future, at the cost of more computer time. The same
goes for 2D axisymmetry vs.\ full 3D---the only difference is computer time, and
our future calculations will explore the 3D evolution and compare to
the 2D simulations presented here. In particular, in 3D we will be
able to explore shear instabilities at the flame front.  We can also
capture the baroclinic instability \citep{Cavecchi2019} and the
competition between it and shear.  Larger networks are a
straightforward change, and already supported in \castro\ using the
\pynucastro\ framework~\citep{pynucastro} and JINA ReacLib rate
database~\citep{reaclib}.

@@

In addition to exploring other aspects of the XRB physics, there are several changes to the algorithm used to
model these XRBs we will pursue.  First, as shown in \citet{castro-sdc}, we have
developed a fourth-order (in space and time) method for coupling
hydrodynamics and reactions that should greatly improve the accuracy
of the simulations.  We expect that by using this new high-order
algorithm we can drop a level of refinement from the simulations while
still accurately modeling the evolution.  We have also ported
\castro\ to GPUs, giving an order of magnitude performance boost on
nodes with both CPUs and GPUs.  Flames without any boosting are currently running
using the new GPU-enabled \castro.
